### 2013-07-23 miscellaneous/inverse-limit-seminar-summer-2013/inverse-limit-results.tex
Finished wedge inverse limit example

  This shows $K = L \cap \prod_{n<\omega} K_n$. To see that minimal candidates for $K_n$ exist, observe that that if
    \[
      K = L \cap \prod_{n<\omega} K_{n,\lambda}
    \]
  for all $\lambda$ in some indexing set $I$, then if $K^*_n = \bigcap_{\lambda\in I} K_{n,\lambda}$ we may see
    \[
      K = L \cap \prod_{n<\omega} \left(\bigcap_{\lambda\in I} K_{n,\lambda}\right)
    \]
  and thus $K^*_n$ is the minimal subcontinuum for each $n$. ($K^*_n$ is obviously compact, and observe that if it weren't connected, $K$ wouldn't be connected either.)
\end{proof}

@@

If $a_n=0$ and $b_n=1$ always, then $K=L$ and is not a proper subcontinuum, so either:
  \begin{itemize}
    \item We assume $0< a_N < b_N \leq 1$ and observe by the minimality of $[a_{N+1},b_{N+1}]$ and $f(1-\frac{a_N}{2})=a_N$ that $[a_{N+1},b_{N+1}]\subseteq[a_{N+1},1-\frac{a_N}{2}]$, which implies $0\leq a_{N+1} < b_{N+1} \leq 1 - \frac{a_N}{2} < 1$.
    \item We get $0\leq a_N < b_N < 1$ for free.
  \end{itemize}

Then one of the following occurs:
  \begin{itemize}
    \item We may find $N$ such that $0<a_N<b_N<1$.
  \end{itemize}
\end{proof}

>>>>

  This shows $K = L \cap \prod_{n<\omega} K_n$. To see that minimal candidates for $K_n$ exist, observe that that if
    \[
      K = L \cap \prod_{n<\omega} K_{n,\lambda}
    \]
  for all $\lambda$ in some indexing set $I$, then if $K^*_n = \bigcap_{\lambda\in I} K_{n,\lambda}$ we may see
    \[
      K = L \cap \prod_{n<\omega} K^*_n
    \]
  and thus $K^*_n$ is the minimal subcontinuum for each $n$. ($K^*_n$ is obviously compact, and observe that if it weren't connected, $K$ wouldn't be connected either.)
\end{proof}

@@

If $a_n=0$ and $b_n=1$ always, then $K=L$ and is not a proper subcontinuum, so either:
  \begin{itemize}
    \item We assume $0< a_N < b_N \leq 1$ and observe by the minimality of $[a_{N+1},b_{N+1}]$ and $f(1-\frac{a_N}{2})=a_N$ that $[a_{N+1},b_{N+1}]\subseteq[a_{N+1},1-\frac{a_N}{2}]$, which implies $0\leq a_{N+1} < b_{N+1} \leq 1 - \frac{a_N}{2} < 1$.
    \item We have $0\leq a_N < b_N < 1$ for free.
  \end{itemize}
Then one of the following occurs:
  \begin{itemize}
    \item Suppose $b_{N+1}=1$; then $a_{N+2}>0$. In this case, the reader may check that each sequence in $K$ has a unique value in the $(N+2)^{th}$ coordinate - if not, then the sequences must ``branch'' in some $M>N+2$ coordinate, but either $b_M<\frac{1}{2}$ or $a_M>\frac{1}{2}$ prevents such branching.
    \item It may be that $0=a_n$ for all $n<\omega$. Then the reader may again check that each sequence in $K$ has a unique value in the $(N+2)^{th}$ coordinate where $0=a_{N+2}<b_{N+2}<1$, as $M>N+2 \Rightarrow b_M<\frac{1}{2}$ prevents branching.
  \end{itemize}

It may be easily verified then that the projection $\pi_{N+2}$ is a homeomorphism from $K$ to $[a_{N+2},b_{N+2}]$.
\end{proof}
